A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-06 methodology.tex
reedit

For each cluster, we read the code and the bug reports of the datapoints (if they existed). If we judged that the members of a cluster fit into a pattern, we wrote a natural language description of that cluster. Considering the descriptions, we linked similar clusters together as possible candidates for merging, and removed the datapoints that did not fit into the first two groups listed above. We considered these candidates and carried out appropriate ones. Finally, we selected 20 of the remaining clusters---the ones that manifested more-specific changes. Sections~\ref{sec:common_patterns}~and~\ref{sec:bc_patterns} present our clusters.

>>>>

For each cluster, we read the code and the bug reports of the datapoints (if they existed). If we judged that the members of a cluster fit into a pattern, we wrote a natural language description of that cluster. Considering the descriptions, we linked similar clusters together as possible candidates for merging, and removed the datapoints that were not either bug-fix or fix-inducing. We considered these candidates and carried out appropriate ones. Finally, we selected 20 of the remaining clusters---the ones that manifested more-specific changes. Sections~\ref{sec:common_patterns}~and~\ref{sec:bc_patterns} present our clusters.

### 2023-06-06 results.tex
reedit

\noindent\textbf{Actionability of adding Option to a type:} When the user's specification requires a variable to be able to assume \texttt{None} values, these patterns indicate the need to modify the program accordingly. A program repair tool can leverage these patterns to automatically update the variable's type to \texttt{Option<T>}, ensuring that it can now hold \texttt{None} as a valid value. This pattern is a part of a \textit{fix-induced} change, thus, a repair tool should also systematically update other occurrences of that variable throughout the program to account for the change and ensure program correctness.

>>>>

\noindent\textbf{Actionability of adding Option to a type:} This pattern occurs as a \textit{fix-induced} change---a repair tool might be carrying out a broader change and need to make smaller changes like this one in the process. Our empirical results suggest that this type of change does occur in practice and will need to be part of a program repair tool's arsenal.
